---
title: "L. major Ryan infecting Sandfly: UTR Length and Alternative Trans-splicing / Polyadenylation Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
  pdf_document:
    toc: true
    latex_engine: xelatex
---

```{r knitr_settings, include=FALSE}
library(knitr)
opts_chunk$set(fig.width=1600/192,
               fig.height=1200/192,
               fig.retina=1,
               dpi=192)
options(knitr.duplicate.label='allow')

# If rmarkdown.pandoc.to not specified (for example, when kniting
# piece-by-piece in Vim-R), have it default to 'latex' output.
if (is.null(opts_knit$get("rmarkdown.pandoc.to"))) {
    opts_knit$set(rmarkdown.pandoc.to='latex')
}

# Clean up any existing variables
rm(list=ls())

# Create output and build directories if needed
for (x in c('build', 'output')) {
    if (!file.exists(x)) {
        dir.create(x)
    }
}
```

Overview
========

The goal of this analysis is to parse the output from our [UTR analysis
pipeline](https://github.com/elsayed-lab/utr_analysis), analyze spliced leader
acceptor site and poly-adenylation site counts, and determine the most likely
primary UTR boundaries for each gene where information is available.

5'- and 3'-UTR boundaries, along with some other useful information such as UTR
GC- and CT-richness are outputted in a format that is convenient for downstream
analysis.

Finally, we will look for evidence of either alternative trans-splicing or
poly-adenylation and attempt to visualize the prevalence and magnitude of
these events across the different developmental stages.

This analysis is based on a version originally written and applied separately
to *T. cruzi* and *L. major* in 2014. The code has been refactored and cleaned
up to make it easier to apply to new datasets.

Settings
========

```{r child='settings/lmajor_sacks.Rmd'}
```

```{r include=FALSE}
outdir <- file.path('output', outfile_prefix)
if (!dir.exists(outdir)) {
    dir.create(outdir)
}
```

Methods
=======

## Libraries

```{r load_libraries, message=FALSE, warning=FALSE, include=verbose}
library('GenomicRanges')
library('Biostrings')
library('rtracklayer')
library('ggplot2')
library('ggvis')
library('reshape2')
library('dplyr')
source('helper.R')
```

```{r child='child/load_data.Rmd'}
```

## Methods and Results

### 5'UTR

```{r utr5_settings, include=FALSE}
feature_name <- 'sl'
gffs         <- sl_gffs
```

```{r child='child/utr_length.Rmd'}
```

```{r child='child/utr_composition.Rmd'}
```

```{r child='child/results.Rmd'}
```

### 3'UTR

```{r utr3_settings, include=FALSE}
gffs         <- polya_gffs
feature_name <- 'polya'
```

```{r child='child/utr_length.Rmd'}
```

```{r child='child/utr_composition.Rmd'}
```

```{r child='child/results.Rmd'}
```

Downloads
=========

```{r, echo=FALSE, results='asis'}
cat('\n')

for (x in list.files(outdir)) {
    cat(sprintf("- [%s](%s)\n", x, x))
}
```

```{r save_output, include=FALSE}
timestring <- format(Sys.time(), "%Y-%m-%d")
html_filepath <- file.path(outdir, sprintf("%s_%s.html", outfile_prefix, timestring))
system(sprintf('(sleep 30 && cp README.html %s) &', html_filepath))
```

System Information
==================

```{r sysinfo, results='asis'}
if (opts_knit$get("rmarkdown.pandoc.to") == 'latex') {
    toLatex(sessionInfo())
} else {
    library('pander')
    pander(sessionInfo())
}
```
